Modeling vertical-axis cross-flow turbine wakes

### 2015-08-11 paper.tex
Add performance results and approximate computation times for CFD cases; closes #13

The $k$--$\omega$ SST and Spalart--Allmaras RANS model cases were verified for
convergence of the turbine mean power coefficient with respect to grid spacing
and timestep. The grid topology was fixed, but the number of cells per unit
length were scaled proportionally, maintaining the same background mesh cell
aspect ratio. Results for this parameter sweep are shown in 
Figure~\ref{fig:spatial-grid-dep}, from which the final number of streamwise
grid points $N_x = 70$ was chosen.

@@

@@

Predictions for both the power and drag coefficients are shown in Figure~\ref{fig:perf-comp}

\begin{figure}[ht]
\caption{Power (a) and drag (b) coefficient predictions from experiments and
each numerical model.}
\label{fig:perf-comp}
\end{figure}

\todo[inline]{Add bar graph comparing various performance results for the RVAT.}

>>>>

The $k$--$\omega$ SST and Spalart--Allmaras RANS model cases were verified for
convergence of the turbine mean power coefficient with respect to grid spacing
and timestep. The grid topology was fixed, but the number of cells per unit
length were scaled proportionally, maintaining the same background mesh cell
aspect ratio. Results for this parameter sweep are shown in 
Figure~\ref{fig:spatial-grid-dep}, from which the final number of streamwise
grid points $N_x = 70$ was chosen. This corresponds to a total cell count of approximately $5 \times 10^4$ for the 2-D cases and 
\todo[inline]{Get total cell count for 3-D case.}

@@

Computations for the 3-D cases were run on 192 processes and took on the order
of 1,000 CPU hours per second of simulation time. The 2-D simulations were run
on a single processor and took on the order of one CPU hour per second.

@@

Predictions for both the mean rotor power and drag coefficients are shown in
Figure~\ref{fig:perf-comp}. In general, the 2-D CFD cases both overpredict
turbine loading, which is likely due to their increased blockage ratio,
unresolved blade end effects, and lack of blade support struts.

The 3-D simulations fair better at predicting the experimental measurements,
with the Spalart--Allmaras model performing relatively better. The apparent
overprediction of rotor drag coefficient could be an effect of the experimental
procedure, where the ``tare drag'' from the turbine mounting structure was
measured without a turbine installed, then subtracted in post-processing.
Technically the local flow field will have changed, and hence the tare drag will
change as well.

\begin{figure}[ht]
    \includegraphics[width=0.9\textwidth]{figures/perf_bar_chart} \caption{Power
        (left) and drag (right) coefficient predictions from experiments and each
        numerical model.} \label{fig:perf-comp}
\end{figure}
